### 2022-01-17 README.Rmd
Add umag hyperlink and about section

The purpose of the {ASQ3} package is to provide access to the data collected by the Centro Asistencial Docente e Investigación de la Universidad de Magallanes (CADI-UMAG).

@@

>>>>

The purpose of the {ASQ3} package is to provide access to the data collected by the Centro Asistencial Docente e Investigación de la [Universidad de Magallanes](http://www.umag.cl/) (CADI-UMAG).

@@

## About <i class="fab fa-r-project"></i>

R is a high-level statistical programming language used for data analysis, as well as for the development of software tools such as websites, reports, applications, digital books, etc. For more information you can visit the [R-project](https://www.r-project.org/about.html) website.
